---
title: "daiquiri data quality report"
output: 
  html_document:
    df_print: paged
params:
  sourcedata: sourcedata
  aggregatedata: aggregatedata
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
knitr::opts_chunk$set(comment = NA)
knitr::opts_chunk$set(rownames.print = FALSE)
```

```{css, echo=FALSE}
h1.title {
	font-size: 28px;
	}
p.compact {
	margin-bottom: 0px;
	margin-top: 0px;
	}
```

<p class="compact">
Dataset: **`r encodeString(params$sourcedata$dataset_shortdesc)`**
</p>

<p class="compact">
Aggregated by: **`r params$aggregatedata$aggregation_timeunit`**
</p>

<p class="compact">
Report created on: `r Sys.time()`; Package version `r utils::packageVersion(utils::packageName())`; `r R.Version()$version.string`
</p>

# {.tabset .tabset-pills}

## Source data {.tabset}


```{r sourcedata}
sourcesummary <- summarise_source_data(params$sourcedata, showprogress = FALSE)
sourcedatafields <- sourcesummary$datafields
sourcedatafields$ordinal_position <- seq.int(nrow(sourcedatafields))
```

### Data fields imported

```{r fields-imported}

reactable::reactable(
  # NOTE: trimws() needed as summarise_source_data() is optimised for console printout
  sourcedatafields[which(trimws(sourcesummary$datafields$fieldtype) != "ignore"), ],
  sortable = TRUE,
  filterable = FALSE,
  searchable = FALSE,
  rownames = FALSE,
  pagination = FALSE,
  striped = TRUE,
  highlight = TRUE,
  columns = list(
    fieldname = reactable::colDef(
      name = "Field name",
      style = list(fontWeight = "bold")
    ),
    fieldtype = reactable::colDef(name = "Field type"),
    datatype = reactable::colDef(show = FALSE),
    count = reactable::colDef(name = "Total values"),
    missing = reactable::colDef(name = "Missing values"),
    min = reactable::colDef(name = "Min value"),
    max = reactable::colDef(name = "Max value"),
    validation_warnings = reactable::colDef(name = "Validation warnings"),
    ordinal_position = reactable::colDef(name = "Column position")
  )
)
```


### Data fields ignored

```{r fields-ignored}

reactable::reactable(
  # NOTE: trimws() needed as summarise_source_data() is optimised for console printout
  sourcedatafields[
    which(trimws(sourcesummary$datafields$fieldtype) == "ignore"),
    c("fieldname", "fieldtype", "ordinal_position")
  ],
  sortable = TRUE,
  filterable = FALSE,
  searchable = FALSE,
  pagination = FALSE,
  rownames = FALSE,
  compact = TRUE,
  fullWidth = FALSE,
  columns = list(
    fieldname = reactable::colDef(
      name = "Field name",
      minWidth = 200
    ),
    fieldtype = reactable::colDef(
      name = "Field type",
      minWidth = 100
    ),
    ordinal_position = reactable::colDef(name = "Column position")
  )
)
```


### Validation warnings

```{r validation-warnings}

reactable::reactable(
  sourcesummary$validation_warnings,
  sortable = TRUE,
  filterable = FALSE,
  searchable = FALSE,
  rownames = FALSE,
  pagination = FALSE,
  striped = TRUE,
  highlight = TRUE,
  compact = TRUE,
  fullWidth = FALSE,
  columns = list(
    fieldname = reactable::colDef(
      name = "Field name",
      style = list(fontWeight = "bold"),
      minWidth = 200
    ),
    message = reactable::colDef(
      name = "Details",
      minWidth = 500
    ),
    instances = reactable::colDef(name = "Instances")
  )
)
```

### Summary

```{r sourcedata-summary}

summarydf <- data.frame(
  "Item" = c(
    "Columns in source",
    "Columns imported",
    "Column used for timepoint",
    "Min timepoint value",
    "Max timepoint value",
    "Rows in source",
    "Duplicate rows",
    "Rows missing timepoint values",
    "Rows imported",
    "Strings interpreted as missing values",
    "Total validation warnings"
  ),
  "Value" = c(
    sourcesummary$overall["cols_source_n"],
    sourcesummary$overall["cols_imported_n"],
    sourcesummary$overall["timepoint_fieldname"],
    sourcesummary$overall["timepoint_min"],
    sourcesummary$overall["timepoint_max"],
    sourcesummary$overall["rows_source_n"],
    sourcesummary$overall["rows_duplicates_n"],
    sourcesummary$overall["timepoint_missing_n"],
    sourcesummary$overall["rows_imported_n"],
    sourcesummary$overall["na_values"],
    sum(sourcesummary$validation_warnings$instances, na.rm = TRUE) +
      sum(is.na(
        sourcesummary$validation_warnings$instances
      ))
  ),
  stringsAsFactors = FALSE
)

reactable::reactable(
  summarydf,
  sortable = FALSE,
  filterable = FALSE,
  searchable = FALSE,
  pagination = FALSE,
  rownames = FALSE,
  striped = TRUE,
  compact = TRUE,
  fullWidth = FALSE,
  columns = list(
    Item = reactable::colDef(
      name = "",
      style = list(fontWeight = "bold"),
      minWidth = 300
    ),
    Value = reactable::colDef(
      name = "",
      minWidth = 200
    )
  )
)
```


## Aggregated data {.tabset}


```{r aggregatedata}
aggsummary <- summarise_aggregated_data(params$aggregatedata)
```


### Values present

```{r overview-presence}

plot_overview_combo_static(
  aggfields = params$aggregatedata$aggregatefields,
  aggtype = "n",
  lineplot_fieldname = params$aggregatedata$timepoint_fieldname,
  lineplot_fillcolour = "pink",
  heatmap_fillcolour = "darkred",
  title = paste("Records per", params$aggregatedata$aggregation_timeunit)
)
```

### Missing values

```{r overview-missing}

plot_overview_combo_static(
  aggfields = params$aggregatedata$aggregatefields,
  aggtype = "missing_n",
  lineplot_fieldname = "[ALLFIELDSCOMBINED]",
  lineplot_fillcolour = "lightblue",
  heatmap_fillcolour = "darkblue",
  title = paste(
    "Total missing values per",
    params$aggregatedata$aggregation_timeunit
  )
)
```

### Non-conformant values

```{r overview-nonconformant}

plot_overview_combo_static(
  aggfields = params$aggregatedata$aggregatefields,
  aggtype = "nonconformant_n",
  lineplot_fieldname = "[ALLFIELDSCOMBINED]",
  lineplot_fillcolour = "lightgreen",
  heatmap_fillcolour = "darkgreen",
  title = paste(
    "Total nonconformant values per",
    params$aggregatedata$aggregation_timeunit
  )
)
```

### Duplicate records

```{r overview-duplicates}

plot_overview_totals_static(
  aggfield = params$aggregatedata$aggregatefields[["[DUPLICATES]"]],
  aggtype = "sum",
  fillcolour = "yellow",
  title = paste(
    "Total duplicate records per",
    params$aggregatedata$aggregation_timeunit
  )
)
```

### Summary

```{r aggregatedata-summary}

aggsummarydf <- data.frame(
  "Item" = c(
    "Column used for timepoint",
    "Min timepoint value",
    "Max timepoint value",
    "Timepoint aggregation unit",
    "Total number of timepoints",
    "Number of empty timepoints",
    "Number of data fields"
  ),
  "Value" = c(
    aggsummary$overall["timepoint_fieldname"],
    aggsummary$overall["timepoint_min"],
    aggsummary$overall["timepoint_max"],
    aggsummary$overall["aggregation_timeunit"],
    aggsummary$overall["n_timepoints"],
    aggsummary$overall["n_empty_timepoints"],
    aggsummary$overall["n_fields"]
  ),
  stringsAsFactors = FALSE
)

reactable::reactable(
  aggsummarydf,
  sortable = FALSE,
  filterable = FALSE,
  searchable = FALSE,
  pagination = FALSE,
  rownames = FALSE,
  striped = TRUE,
  compact = TRUE,
  fullWidth = FALSE,
  columns = list(
    Item = reactable::colDef(
      name = "",
      style = list(fontWeight = "bold"),
      minWidth = 300
    ),
    Value = reactable::colDef(
      name = "",
      minWidth = 200
    )
  )
)
```

## Individual data fields {.tabset}

```{r individual-fields, results = 'asis'}
for (i in seq_along(names(params$aggregatedata$aggregatefields))) {
  cat(
    "\n###",
    names(params$aggregatedata$aggregatefields)[i],
    " {.tabset}\n"
  )
  aggtypes <-
    names(params$aggregatedata$aggregatefields[[i]]$values)[-1]
  for (aggtype in aggtypes) {
    cat("\n####", aggtype_friendlyname(aggtype, "short"), "\n")
    p <-
      plot_timeseries_static(
        aggfield = params$aggregatedata$aggregatefields[[i]],
        aggtype = aggtype
      )

    print(p)
    cat("\n")
  }
}
```

