---
title: "daiquiri report"
output: 
  html_document:
    df_print: paged
params:
  sourcedata: sourcedata
  aggregatedata: aggregatedata
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
knitr::opts_chunk$set(comment = NA)
knitr::opts_chunk$set(rownames.print = FALSE)

```

Dataset: **`r encodeString(params$sourcedata$sourcename)`**

Aggregated by: **`r params$aggregatedata$aggregation_timeunit`**

Report created on: `r Sys.time()`

# {.tabset .tabset-pills}

## Raw data {.tabset}


```{r sourcedata}
sourcesummary <- summarise_source_data(params$sourcedata, showprogress = FALSE)
sourcedatafields <- sourcesummary$datafields
sourcedatafields$ordinal_position <- seq.int(nrow(sourcedatafields))
```

### Data fields imported

```{r fields-imported}

reactable::reactable(sourcedatafields[which(sourcesummary$datafields$fieldtype != "ignore"),],
				sortable = TRUE,
				filterable = FALSE,
				searchable = FALSE,
				rownames = FALSE,
				pagination = FALSE,
				striped = TRUE,
				highlight = TRUE,
				columns = list(
					fieldname = reactable::colDef(name = "Field name",
														 style = list(fontWeight = "bold")),
					fieldtype = reactable::colDef(name = "Field type"),
					datatype = reactable::colDef(name = "Datatype"),
					count = reactable::colDef(name = "Total values"),
					missing = reactable::colDef(name = "Missing values"),
					min = reactable::colDef(name = "Min value"),
					max = reactable::colDef(name = "Max value"),
					validation_warnings = reactable::colDef(name = "Validation warnings"),
					ordinal_position = reactable::colDef(name = "Column position")
					)
				)
```


### Data fields ignored

```{r fields-ignored}

reactable::reactable(sourcedatafields[which(sourcesummary$datafields$fieldtype == "ignore"), c("fieldname","fieldtype","ordinal_position")],
				sortable = TRUE,
				filterable = FALSE,
				searchable = FALSE,
				pagination = FALSE,
				rownames = FALSE,
				compact = TRUE,
				fullWidth = FALSE,
				columns = list(
					fieldname = reactable::colDef(name = "Field name",
														 minWidth = 200),
					fieldtype = reactable::colDef(name = "Field type",
														 minWidth = 100),
					ordinal_position = reactable::colDef(name = "Column position")
					)
				)
```


### Validation warnings

```{r validation-warnings}

reactable::reactable(sourcesummary$validation_warnings,
				sortable = TRUE,
				filterable = FALSE,
				searchable = FALSE,
				rownames = FALSE,
				pagination = FALSE,
				striped = TRUE,
				highlight = TRUE,
				compact = TRUE,
				fullWidth = FALSE,
				columns = list(
					fieldname = reactable::colDef(name = "Field name",
														 style = list(fontWeight = "bold"),
														 minWidth = 200),
					colindex = reactable::colDef(name = "Column position"),
					rowindex = reactable::colDef(name = "Row position"),
					message = reactable::colDef(name = "Details",
													 minWidth = 500)
					)
				)

```

### Summary

```{r sourcedata-summary}
summarydf <- data.frame("Item" = c("Columns in source",
																	"Columns imported",
																	"Column used for timepoint",
																	"Min timepoint value",
																	"Max timepoint value",
																	"Rows in source",
																	"Duplicate rows",
																	"Rows missing timepoint values",
																	"Rows imported",
																	"Total validation warnings"),
												"Value" = c(sourcesummary$overall["cols_source_n"],
																		sourcesummary$overall["cols_imported_n"],
																		sourcesummary$overall["timepoint_fieldname"],
																		sourcesummary$overall["timepoint_min"],
																		sourcesummary$overall["timepoint_max"],
																		sourcesummary$overall["rows_source_n"],
																		sourcesummary$overall["rows_duplicates_n"],
																		sourcesummary$overall["timepoint_missing_n"],
																		sourcesummary$overall["rows_imported_n"],
																		nrow(sourcesummary$validation_warnings)),
												stringsAsFactors = FALSE
)
									 


reactable::reactable(summarydf,
					sortable = FALSE,
					filterable = FALSE,
					searchable = FALSE,
					pagination = FALSE,
					rownames = FALSE,
					striped = TRUE,
					compact = TRUE,
					fullWidth = FALSE,
					columns = list(
						Item = reactable::colDef(name = "",
													style = list(fontWeight = "bold"),
													minWidth = 300),
						Value = reactable::colDef(name = "",
													 minWidth = 200)
						)
					)

```


## Aggregated data {.tabset}


```{r aggregatedata}
	aggsummary <- summarise_aggregated_data(params$aggregatedata)
```


### Data presence

```{r overview-presence}
#, fig.height = 0.5*as.numeric(aggsummary$overall["n_fields"])+3

plot_overview_combo_static(aggfields = params$aggregatedata$aggregatefields, 
													 aggtype = "n", 
													 lineplot_fieldname = params$aggregatedata$timepoint_fieldname,
													 lineplot_fillcolour = "pink", 
													 heatmap_fillcolour = "darkred", 
													 title = paste("Records per", params$aggregatedata$aggregation_timeunit))
	

```

### Missing values

```{r overview-missing}

plot_overview_combo_static(aggfields = params$aggregatedata$aggregatefields, 
													 aggtype = "missing_n", 
													 lineplot_fieldname = "ALLFIELDSCOMBINED",
													 lineplot_fillcolour = "lightblue", 
													 heatmap_fillcolour = "darkblue", 
													 title = paste("Total missing values per", params$aggregatedata$aggregation_timeunit))


```

### Non-conformant values

```{r overview-nonconformant}

plot_overview_combo_static(aggfields = params$aggregatedata$aggregatefields, 
													 aggtype = "nonconformant_n", 
													 lineplot_fieldname = "ALLFIELDSCOMBINED",
													 lineplot_fillcolour = "lightgreen", 
													 heatmap_fillcolour = "darkgreen", 
													 title = paste("Total nonconformant values per", params$aggregatedata$aggregation_timeunit))


```

### Duplicate records

```{r overview-duplicates}

plot_overview_totals_static(aggfield = params$aggregatedata$aggregatefields[["DUPLICATES"]], 
													aggtype = "sum",
													fillcolour = "yellow",
													title = paste("Total duplicate records per", params$aggregatedata$aggregation_timeunit))


```

### Summary

```{r aggregatedata-summary}
aggsummarydf <- data.frame("Item" = c("Column used for timepoint",
																			"Min timepoint value",
																			"Max timepoint value",
																			"Timepoint aggregation unit",
																			"Total number of timepoints",
																			"Number of empty timepoints",
																			"Number of data fields"
																			# NOTE: Partitionfield functionality disabled until we work out how to present it
																			# "Column(s) used as partitionfield"
																			),
													 "Value" = c(aggsummary$overall["timepoint_fieldname"],
													 						aggsummary$overall["timepoint_min"],
													 						aggsummary$overall["timepoint_max"],
													 						aggsummary$overall["aggregation_timeunit"],
													 						aggsummary$overall["n_timepoints"],
													 						aggsummary$overall["n_empty_timepoints"],
													 						aggsummary$overall["n_fields"]
													 						# NOTE: Partitionfield functionality disabled until we work out how to present it
													 						# aggsummary$overall["partitionfield_fieldnames"]
													 						),
													 stringsAsFactors = FALSE
)

reactable::reactable(aggsummarydf,
					sortable = FALSE,
					filterable = FALSE,
					searchable = FALSE,
					pagination = FALSE,
					rownames = FALSE,
					striped = TRUE,
					compact = TRUE,
					fullWidth = FALSE,
					columns = list(
						Item = reactable::colDef(name = "",
													style = list(fontWeight = "bold"),
													minWidth = 300),
						Value = reactable::colDef(name = "",
													 minWidth = 200)
						)
					)

```

## Individual data fields {.tabset}

```{r individual-fields, results = 'asis'}
#params$aggregatedata <- testcpddata_byday
#aggtype <- "n"
for(i in seq_along(names(params$aggregatedata$aggregatefields))){
  cat('\n###', names(params$aggregatedata$aggregatefields)[i], ' {.tabset}\n')
	aggtypes <- names(params$aggregatedata$aggregatefields[[i]]$values)[-1]
	for(aggtype in aggtypes){
	  cat('\n####', aggtype, '\n')
	  p <- plot_timeseries_static(aggfield = params$aggregatedata$aggregatefields[[i]], aggtype = aggtype)
	  											 
	  print(p)
	  cat('\n')
	}
}
```

