---
title: "`r params$report_title`"
output: 
  html_document:
    df_print: paged
params:
  source_data: source_data
  aggregated_data: aggregated_data
  report_title: report_title
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
knitr::opts_chunk$set(comment = NA)
knitr::opts_chunk$set(rownames.print = FALSE)
```

```{css, echo=FALSE}
h1.title {
	font-size: 28px;
	}
p.compact {
	margin-bottom: 0px;
	margin-top: 0px;
	}
```

<p class="compact">
Dataset: **`r encodeString(params$source_data$dataset_description)`**
</p>

<p class="compact">
Aggregated by: **`r params$aggregated_data$aggregation_timeunit`**
</p>

<p class="compact">
Report created on: `r Sys.time()`; daiquiri version `r utils::packageVersion(utils::packageName())`; `r R.Version()$version.string`
</p>

# {.tabset .tabset-pills}

## Source data {.tabset}


```{r source-data}
sourcesummary <- summarise_source_data(params$source_data,
  show_progress = FALSE
)
source_data_fields <- sourcesummary$data_fields
source_data_fields$ordinal_position <- seq.int(nrow(source_data_fields))
```

### Data fields imported

```{r fields-imported}

reactable::reactable(
  # NOTE: trimws() needed as summarise_source_data() is optimised for console printout
  source_data_fields[
    which(trimws(sourcesummary$data_fields$field_type) != "ignore"),
  ],
  sortable = TRUE,
  filterable = FALSE,
  searchable = FALSE,
  rownames = FALSE,
  pagination = FALSE,
  striped = TRUE,
  highlight = TRUE,
  columns = list(
    field_name = reactable::colDef(
      name = "Field name",
      style = list(fontWeight = "bold")
    ),
    field_type = reactable::colDef(name = "Field type"),
    datatype = reactable::colDef(show = FALSE),
    count = reactable::colDef(name = "Total values"),
    missing = reactable::colDef(name = "Missing values"),
    min = reactable::colDef(name = "Min value"),
    max = reactable::colDef(name = "Max value"),
    validation_warnings = reactable::colDef(name = "Validation warnings"),
    ordinal_position = reactable::colDef(name = "Column position")
  )
)
```


### Data fields ignored

```{r fields-ignored}

reactable::reactable(
  # NOTE: trimws() needed as summarise_source_data() is optimised for console printout
  source_data_fields[
    which(trimws(sourcesummary$data_fields$field_type) == "ignore"),
    c("field_name", "field_type", "ordinal_position")
  ],
  sortable = TRUE,
  filterable = FALSE,
  searchable = FALSE,
  pagination = FALSE,
  rownames = FALSE,
  compact = TRUE,
  fullWidth = FALSE,
  columns = list(
    field_name = reactable::colDef(
      name = "Field name",
      minWidth = 200
    ),
    field_type = reactable::colDef(
      name = "Field type",
      minWidth = 100
    ),
    ordinal_position = reactable::colDef(name = "Column position")
  )
)
```


### Validation warnings

```{r validation-warnings}

reactable::reactable(
  sourcesummary$validation_warnings,
  sortable = TRUE,
  filterable = FALSE,
  searchable = FALSE,
  rownames = FALSE,
  pagination = FALSE,
  striped = TRUE,
  highlight = TRUE,
  compact = TRUE,
  fullWidth = FALSE,
  columns = list(
    field_name = reactable::colDef(
      name = "Field name",
      style = list(fontWeight = "bold"),
      minWidth = 200
    ),
    message = reactable::colDef(
      name = "Details",
      minWidth = 500
    ),
    instances = reactable::colDef(name = "Instances")
  )
)
```

### Summary

```{r source-data-summary}

summarydf <- data.frame(
  "Item" = c(
    "Columns in source",
    "Columns imported",
    "Column used for timepoint",
    "Min timepoint value",
    "Max timepoint value",
    "Rows in source",
    "Duplicate rows",
    "Rows missing timepoint values",
    "Rows imported",
    "Strings interpreted as missing values",
    "Total validation warnings"
  ),
  "Value" = c(
    sourcesummary$overall["cols_source_n"],
    sourcesummary$overall["cols_imported_n"],
    sourcesummary$overall["timepoint_field_name"],
    sourcesummary$overall["timepoint_min"],
    sourcesummary$overall["timepoint_max"],
    sourcesummary$overall["rows_source_n"],
    sourcesummary$overall["rows_duplicates_n"],
    sourcesummary$overall["timepoint_missing_n"],
    sourcesummary$overall["rows_imported_n"],
    sourcesummary$overall["na_values"],
    sum(sourcesummary$validation_warnings$instances, na.rm = TRUE) +
      sum(is.na(
        sourcesummary$validation_warnings$instances
      ))
  ),
  stringsAsFactors = FALSE
)

reactable::reactable(
  summarydf,
  sortable = FALSE,
  filterable = FALSE,
  searchable = FALSE,
  pagination = FALSE,
  rownames = FALSE,
  striped = TRUE,
  compact = TRUE,
  fullWidth = FALSE,
  columns = list(
    Item = reactable::colDef(
      name = "",
      style = list(fontWeight = "bold"),
      minWidth = 300
    ),
    Value = reactable::colDef(
      name = "",
      minWidth = 200
    )
  )
)
```


## Aggregated data {.tabset}


```{r aggregated-data}
aggsummary <- summarise_aggregated_data(params$aggregated_data)
```


### Values present

```{r overview-presence}

plot_overview_combo_static(
  agg_fields = params$aggregated_data$aggregated_fields,
  agg_fun = "n",
  lineplot_field_name = params$aggregated_data$timepoint_field_name,
  lineplot_fill_colour = "pink",
  heatmap_fill_colour = "darkred",
  title = paste("Records per", params$aggregated_data$aggregation_timeunit)
)
```

### Missing values

```{r overview-missing}

plot_overview_combo_static(
  agg_fields = params$aggregated_data$aggregated_fields,
  agg_fun = "missing_n",
  lineplot_field_name = "[ALL_FIELDS_COMBINED]",
  lineplot_fill_colour = "lightblue",
  heatmap_fill_colour = "darkblue",
  title = paste(
    "Total missing values per",
    params$aggregated_data$aggregation_timeunit
  )
)
```

### Non-conformant values

```{r overview-nonconformant}

plot_overview_combo_static(
  agg_fields = params$aggregated_data$aggregated_fields,
  agg_fun = "nonconformant_n",
  lineplot_field_name = "[ALL_FIELDS_COMBINED]",
  lineplot_fill_colour = "lightgreen",
  heatmap_fill_colour = "darkgreen",
  title = paste(
    "Total nonconformant values per",
    params$aggregated_data$aggregation_timeunit
  )
)
```

### Duplicate records

```{r overview-duplicates}

plot_overview_totals_static(
  agg_field = params$aggregated_data$aggregated_fields[["[DUPLICATES]"]],
  agg_fun = "sum",
  fill_colour = "yellow",
  title = paste(
    "Total duplicate records per",
    params$aggregated_data$aggregation_timeunit
  )
)
```

### Summary

```{r aggregated-data-summary}

aggsummarydf <- data.frame(
  "Item" = c(
    "Column used for timepoint",
    "Min timepoint value",
    "Max timepoint value",
    "Timepoint aggregation unit",
    "Total number of timepoints",
    "Number of empty timepoints",
    "Number of data fields"
  ),
  "Value" = c(
    aggsummary$overall["timepoint_field_name"],
    aggsummary$overall["timepoint_min"],
    aggsummary$overall["timepoint_max"],
    aggsummary$overall["aggregation_timeunit"],
    aggsummary$overall["n_timepoints"],
    aggsummary$overall["n_empty_timepoints"],
    aggsummary$overall["n_fields"]
  ),
  stringsAsFactors = FALSE
)

reactable::reactable(
  aggsummarydf,
  sortable = FALSE,
  filterable = FALSE,
  searchable = FALSE,
  pagination = FALSE,
  rownames = FALSE,
  striped = TRUE,
  compact = TRUE,
  fullWidth = FALSE,
  columns = list(
    Item = reactable::colDef(
      name = "",
      style = list(fontWeight = "bold"),
      minWidth = 300
    ),
    Value = reactable::colDef(
      name = "",
      minWidth = 200
    )
  )
)
```

## Individual data fields {.tabset}

```{r individual-fields, results = 'asis'}
for (i in seq_along(names(params$aggregated_data$aggregated_fields))) {
  cat(
    "\n###",
    names(params$aggregated_data$aggregated_fields)[i],
    " {.tabset}\n"
  )
  agg_funs <-
    params$aggregated_data$aggregated_fields[[i]]$function_list
  for (agg_fun in agg_funs) {
    if (startsWith(agg_fun, "subcat")) {
      cat("\n####", agg_fun_friendly_name(agg_fun, "short"), " {.tabset}\n")
      # first tab has all subcats in heatmap
      cat("\n#####", "All\n")
      p <-
        plot_subcat_heatmap_static(
          agg_field = params$aggregated_data$aggregated_fields[[i]],
          agg_fun = agg_fun
        )
      print(p)
      cat("\n")
      # following tabs show individual time series
      agg_cols <- names(params$aggregated_data$aggregated_fields[[i]]$values)
      for (subcat_col in agg_cols[which(startsWith(agg_cols, agg_fun))]) {
        cat("\n#####", agg_fun_subcat_value(subcat_col), "\n")
        p <-
          plot_timeseries_static(
            agg_field = params$aggregated_data$aggregated_fields[[i]],
            agg_fun = subcat_col
          )
        print(p)
        cat("\n")
      }
    } else{
      cat("\n####", agg_fun_friendly_name(agg_fun, "short"), "\n")
      p <-
        plot_timeseries_static(
          agg_field = params$aggregated_data$aggregated_fields[[i]],
          agg_fun = agg_fun
        )
      print(p)
      cat("\n")
    }
  }
}
```

